\documentclass[10pt,letterpaper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumitem}
\usepackage{scalerel} % for flexible scaling
\usepackage{hyperref} % for clickable links
\usepackage{etaremune}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{lastpage}

% header and footer
\pagestyle{fancy}
\fancyhead[L]{\textcolor{gray}{Lionel Garcia, curriculum vitae}}
\fancyhead[R]{\textcolor{gray}{page \thepage{} of \pageref*{LastPage}}}
\fancyfoot[C]{}
\renewcommand{\headrulewidth}{0pt} % No line in header
\renewcommand{\footrulewidth}{0pt}

% Set itemize style
\setlist[itemize]{
    label=\scalebox{0.0}{\textbullet},
    left=0.0cm,
    itemsep=0.0em
}

% change enumerate style
\renewcommand{\labelenumi}{\color{lightgray}\theenumi.}
\setlength{\leftmargini}{20pt}

% change hyperref style with url color from an xcolor
\definecolor{myblue}{RGB}{54, 146, 199}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=myblue,
}

% commands for journal abbreviations
\newcommand{\publi}[4]{\item #1 -- #3, #2, #4}
\newcommand{\aj}{AJ}
\newcommand{\mnras}{MNRAS}
\newcommand{\aap}{A\&A}
\newcommand{\procspie}{Proc. SPIE}
\newcommand{\baas}{Bulletin of the AAS}
\newcommand{\pasp}{PASP}

% change section and subsection font size
\titleformat{\section}
{\normalfont\fontsize{12}{15}\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\fontsize{10}{13}\bfseries}{\thesection}{1em}{}

\begin{document}
\thispagestyle{empty}
\noindent
\setlength{\tabcolsep}{0em}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \noindent\textbf{\LARGE Lionel Garcia} & \today \\
    \\
    mail -- \texttt{lgarcia@flatironinstitute.org}\\
    website -- \href{https://lgrcia.github.io/}{\texttt{lgrcia.github.io}} \\
    github -- \href{https://github.com/lgrcia}{\texttt{lgrcia}} \\
\end{tabular*}


\section*{Education}
\begin{itemize}
    \item PhD, Astronomy -- University of Liège, Belgium (2023)
    \item Msc, Computer Science -- University of Bordeaux, France (2017)
    \item Msc, Optical Engineering -- Institut d'Optique, France (2017)
    \item Bs, Physics -- University of Paris-Sud, France (2014)
\end{itemize}
\section*{Positions}
\begin{itemize}
    \item Research Fellow -- CCA, Flatiron Institute, New York, USA (2023 - now)
    \item Teaching Assistant -- University of Liège, Belgium (2019 - 2021)
    \item Young Graduate Trainee -- European Space Agency, Netherlands (2017 - 2018)
    \item Technical Student -- CERN, Switzerland (2016 - 2017)
\end{itemize}
\section*{Teaching \small{at University of Liège}}
\begin{itemize}
    \item Classical Mechanics -- Undergraduate
    \item Mathematical Modeling for the Environment -- Graduate
    \item Astronomical Observations -- Graduate
\end{itemize}
\section*{Grants \& Proposals}
\begin{itemize}
    \item 2024 -- (PI) JWST General Observer program \href{https://www.stsci.edu/jwst/science-execution/program-information?id=5799}{5799}, 22 hours, 205,000 USD
    \item 2024 -- (co-I) JWST Archival Research program \href{https://www.stsci.edu/jwst/science-execution/program-information?id=5370}{5370}, PI Benjamin Rackham, 1,300,000 USD
    \item 2023 -- Flatiron Research Fellowship, Simons Foundation, 210,000 USD
    \item 2023 -- (co-I) HST Archival Legacy program \href{https://www.stsci.edu/cgi-bin/get-proposal-info?id=17551&observatory=HST}{17551}, PI Benjamin Rackham, 530,000 USD
    \item 2021 -- FRIA Doctoral scholarship, FRS–FNRS, 65,000 EURO
\end{itemize}
\section*{Talks \& Workshops}
\begin{itemize}
    \item Dec. 2024 -- Workshop Instructor of PySnacks 7, IAA-CSIC, Granada, Spain
    \item Jul. 2024 -- Talk at TESS Science Conference III, Cambridge, USA
    \item Jun. 2024 -- Seminar at University of Oxford, UK
    \item Oct. 2023 -- Seminar at TESS Team Meeting, Cambridge, USA
    \item Oct. 2023 -- Seminar at EAPS/MIT, Cambridge, USA
    \item May 2023 -- Seminar at IRAP, Toulouse, France
    \item May 2023 -- Seminar at Observatoire de la Côte d'Azur, Nice, France
    \item May 2023 -- Seminar at European Space Agency, Noordwijk, Netherlands
    \item May 2023 -- Seminar at ETH, Zurich, Switzerland
    \item Mar. 2023 -- Seminar for VAST, online
    \item Mar. 2023 -- Talk at EMAC Workshop (NASA), online
    \item Dec. 2022 -- Talk at ESO Belgian Day, Brussels, Belgium
    \item Jul. 2022 -- Talk at NAM 2020, Warwick, UK
    \item May 2022 -- Talk at Exoplanet IV, Las Vegas, USA
    \item May 2020 -- Talk at SAG21 symposium (NASA), online
    \item Jun. 2019 -- Poster at TRAPPIST-1 conference, Liège, Belgium
\end{itemize}
\section*{Software}
\begin{itemize}
    \item \textsf{\href{https://github.com/lgrcia/spotter}{spotter}}: Approximate fluxes and spectra of non-uniform stars
    \item \textsf{\href{https://github.com/exoplanet-dev/jaxoplanet}{jaxoplanet}}: Analytical models of stellar light curves
    \item \textsf{\href{https://github.com/lgrcia/nuance}{nuance}}: Efficient detection of planets transiting active stars
    \item \textsf{\href{https://github.com/lgrcia/prose}{prose}}: Modular image processing pipelines for Astronomy
    \item \textsf{\href{https://github.com/lgrcia/twirl}{twirl}}: Local astrometric plate solving in Python 
\end{itemize}
\section*{Publications}
\subsection*{First author}

\begin{etaremune}
\publi{2024}{\textsf{jaxoplanet}: Hardware-Accelerated Orbits and Stellar Light Curves}
{Garcia, L.~J., Hattori, S., Foreman-Mackey, D.}
{\href{https://raw.githubusercontent.com/lgrcia/paper-jaxoplanet/main/latex/jaxoplanet_draft_20241017.pdf}{In prep.}}


\publi{2024}{\textsf{nuance}: Efficient Detection of Planets Transiting Active Stars}
{Garcia, L.~J., Foreman-Mackey, D., Murray, C.~A., et al.}
{\href{https://ui.adsabs.harvard.edu/abs/2024AJ....167..284G}{\aj, 167, 284}}

\publi{2022}{HST/WFC3 transmission spectroscopy of the cold rocky planet TRAPPIST-1h}
{Garcia L.~J., Moran, S.~E., Rackham, B.~V., et al.}
{\href{https://ui.adsabs.harvard.edu/abs/2022A\&A...665A..19G}{\aap, 665, A19}}

\publi{2022}{\textsf{prose}: a Python framework for modular astronomical images processing}
{Garcia L.~J., Timmermans, Mathilde, Pozuelos, Francisco J. et al.}
{\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.509.4817G/exportcitation}{MNRAS 509 4817-4828}}

\publi{2018}{Validation of a CCD cosmic ray event simulator against Gaia in-orbit data}
{Garcia L., Prod'homme T., Lucsanyi D. et al.}
{\href{http://doi.org/10.1117/12.2314090}{Proc. SPIE 10709}}

\end{etaremune}
\subsection*{Co-author}
\begin{etaremune}
    \publi{2024}{Infrared photometry with InGaAs detectors: First light with SPECULOOS}
    {Pedersen, P.~P., Queloz, D., Garcia, L., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024arXiv241022140P}{arXiv e-prints, arXiv:2410.22140}}

    \publi{2024}{An extended low-density atmosphere around the Jupiter-sized planet WASP-193 b}
    {Barkaoui, K., Pozuelos, F.~J., Hellier, C., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024NatAs...8..909B}{Nature Astronomy, 8, 909}}
    
    \publi{2024}{A roadmap for the atmospheric characterization of terrestrial exoplanets with JWST}
    {TRAPPIST-1 JWST Community Initiative, de Wit, J., Doyon, R., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024NatAs...8..810T}{Nature Astronomy, 8, 810}}
    
    \publi{2024}{CHEOPS in-flight performance. A comprehensive look at the first 3.5 yr of operations}
    {Fortier, A., Simon, A.~E., Broeg, C., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024A\&A...687A.302F}{\aap, 687, A302}}
    
    \publi{2024}{TOI-4336 A b: A temperate sub-Neptune ripe for atmospheric characterization in a nearby triple M-dwarf system}
    {Timmermans, M., Dransfield, G., Gillon, M., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024A\&A...687A..48T}{\aap, 687, A48}}
    
    \publi{2024}{Coriolis darkening in late-type stars. II. Effect of self-sustained magnetic fields in stratified convective envelopes}
    {Pin{\c{c}}on, C., Petitdemange, L., Raynaud, R., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024A\&A...685A.129P}{\aap, 685, A129}}
    
    \publi{2024}{A 1.55 R$_{{\ensuremath{\oplus}}}$ habitable-zone planet hosted by TOI-715, an M4 star near the ecliptic South Pole}
    {Dransfield, G., Timmermans, M., Triaud, A.~H.~M.~J., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024MNRAS.527...35D}{\mnras, 527, 35}}
    
    \publi{2023}{An M dwarf accompanied by a close-in giant orbiter with SPECULOOS}
    {Triaud, A.~H.~M.~J., Dransfield, G., Kagetani, T., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.525L..98T}{\mnras, 525, L98}}
    
    \publi{2023}{TOI-2084 b and TOI-4184 b: Two new sub-Neptunes around M dwarf stars}
    {Barkaoui, K., Timmermans, M., Soubkiou, A., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...677A..38B}{\aap, 677, A38}}
    
    \publi{2023}{TESS discovery of a super-Earth orbiting the M-dwarf star TOI-1680}
    {Ghachoui, M., Soubkiou, A., Wells, R.~D., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...677A..31G}{\aap, 677, A31}}
    
    \publi{2024}{An extended low-density atmosphere around the Jupiter-sized planet WASP-193 b}
    {Barkaoui, K., Pozuelos, F.~J., Hellier, C., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2024NatAs...8..909B}{Nature Astronomy, 8, 909}}
        
    \publi{2023}{TOI-1442 b and TOI-2445 b: Two potentially rocky ultra-short period planets around M dwarfs}
    {Morello, G., Parviainen, H., Murgas, F., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...673A..32M}{\aap, 673, A32}}
    
    \publi{2023}{A super-Earth and a mini-Neptune near the 2:1 MMR straddling the radius valley around the nearby mid-M dwarf TOI-2096}
    {Pozuelos, F.~J., Timmermans, M., Rackham, B.~V., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...672A..70P}{\aap, 672, A70}}
    
    \publi{2023}{Precise near-infrared photometry, accounting for precipitable water vapour at SPECULOOS Southern Observatory}
    {Pedersen, P.~P., Murray, C.~A., Queloz, D., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.518.2661P}{\mnras, 518, 2661}}
    
    \publi{2022}{Two temperate super-Earths transiting a nearby late-type M dwarf}
    {Delrez, L., Murray, C.~A., Pozuelos, F.~J., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2022A\&A...667A..59D}{\aap, 667, A59}}
    
    \publi{2022}{SPECULOOS Northern Observatory: Searching for Red Worlds in the Northern Skies}
    {Burdanov, A.~Y., de Wit, J., Gillon, M., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2022PASP..134j5001B}{\pasp, 134, 105001}}
    
    \publi{2022}{TESS discovery of a sub-Neptune orbiting a mid-M dwarf TOI-2136}
    {Gan, T., Soubkiou, A., Wang, S.~X., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.514.4120G}{\mnras, 514, 4120}}
    
    \publi{2022}{Observation scheduling and automatic data reduction for the Antarctic Telescope, ASTEP+}
    {Dransfield, G., M{\'e}karnia, D., Triaud, A.~H.~M.~J., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2022SPIE12186E..1FD}{\procspie, 12186, 121861F}}
    
    \publi{2022}{A study of flares in the ultra-cool regime from SPECULOOS-South}
    {Murray, C.~A., Queloz, D., Gillon, M., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.513.2615M}{\mnras, 513, 2615}}
    
    \publi{2022}{Complex Modulation of Rapidly Rotating Young M Dwarfs: Adding Pieces to the Puzzle}
    {G{\"u}nther, M.~N., Berardo, D.~A., Ducrot, E., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2022AJ....163..144G}{\aj, 163, 144}}
    
    \publi{2023}{TOI-1442 b and TOI-2445 b: Two potentially rocky ultra-short period planets around M dwarfs}
    {Morello, G., Parviainen, H., Murgas, F., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2023A\&A...673A..32M}{\aap, 673, A32}}
        
    \publi{2022}{TOI-2257 b: A highly eccentric long-period sub-Neptune transiting a nearby M dwarf}
    {Schanche, N., Pozuelos, F.~J., G{\"u}nther, M.~N., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2022A\&A...657A..45S}{\aap, 657, A45}}
    
    \publi{2021}{A large sub-Neptune transiting the thick-disk M4 V TOI-2406}
    {Wells, R.~D., Rackham, B.~V., Schanche, N., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...653A..97W}{\aap, 653, A97}}
    
    \publi{2021}{Six transiting planets and a chain of Laplace resonances in TOI-178}
    {Leleu, A., Alibert, Y., Hara, N.~C., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...649A..26L}{\aap, 649, A26}}
    
    \publi{2021}{SPECULOOS: Ultracool dwarf transit survey. Target list and strategy}
    {Sebastian, D., Gillon, M., Ducrot, E., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2021A\&A...645A.100S}{\aap, 645, A100}}
    
    \publi{2020}{Development of the SPECULOOS exoplanet search project}
    {Sebastian, D., Pedersen, P.~P., Murray, C.~A., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2020SPIE11445E..21S}{\procspie, 11445, 1144521}}
    
    \publi{2020}{{\ensuremath{\pi}} Earth: A 3.14 day Earth-sized Planet from K2's Kitchen Served Warm by the SPECULOOS Team}
    {Niraula, P., Wit, J. de ., Rackham, B.~V., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2020AJ....160..172N}{\aj, 160, 172}}
    
    \publi{2020}{A super-Earth and a sub-Neptune orbiting the bright, quiet M3 dwarf TOI-1266}
    {Demory, B.-O., Pozuelos, F.~J., G{\'o}mez Maqueo Chew, Y., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2020A\&A...642A..49D}{\aap, 642, A49}}
    
    \publi{2020}{GJ 273: on the formation, dynamical evolution, and habitability of a planetary system hosted by an M dwarf at 3.75 parsec}
    {Pozuelos, F.~J., Su{\'a}rez, J.~C., de El{\'\i}a, G.~C., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2020A\&A...641A..23P}{\aap, 641, A23}}
    
    \publi{2020}{Photometry and performance of SPECULOOS-South}
    {Murray, C.~A., Delrez, L., Pedersen, P.~P., et al.}
    {\href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.2446M}{\mnras, 495, 2446}}
\end{etaremune}
\end{document}